---
title: "CA - Session 2: homework"
output:
  html_document:
    df_print: paged
    toc: yes
---

# Homework exercises

- Create two variables and multiply them
```{r}
a <- 2
b <- 3
print(a*b)
```


- Create a sequence with the first 50 even numbers 
```{r}
evenseq <- seq(2, 100, 2)
print(evenseq)
```


- Install the package tidyverse. Check the description of this package and explain why it is an interesting library.
```{r}
install.packages("tidyverse")
```


- Which packages are included in tidyverse?
```{r}
tidyverse::tidyverse_packages()
```


- Create a variable called my_variable that contains the word "TRUE". Determine the class of the object my_variable.
```{r}
my_variable <- "TRUE"
class(my_variable)
```


- Transform my_variable as a logical variable. Determine the class of the object my_variable.
```{r}
my_variable <- TRUE
class(my_variable)
```


- Create a vector (called student) to hold the data of student: name, email, intake and nationaly. Access the element with the name “email”
```{r}
student <- c(name="Ankit", email="ankit.somani@student.ie.edu", intake="IMBA Sep 2019", nationality="Indian")
print(student["email"])
```


- Create a dataframe (called students) to the data of several students: name, email, intake and nationaly. Access the element with the name “email”
```{r}
name <- c("Rafael", "Messi", "Ronaldo", "Pogba", "Rashford")
email <- c("rafael@student.ie.edu", "messi@student.ie.edu", "ronaldo@student.ie.edu", "pogba@student.ie.edu", "rashford@student.ie.edu")
intake <- c("IMBA Sep 2019", "IMBA Sep 2019", "IMBA Sep 2019", "IMBA Sep 2019", "IMBA Sep 2019")
nationality <- c("Spanish", "Argentinian", "Portuguese", "French", "English")
students <- data.frame(name, email, intake, nationality)
print(students["email"])
```


- Create a vector of coefficients, called coeffs, using the sample function. Here, we draw a sample of size 5 from −100, . . . , 100 without replacement

```{r}
coeffs <- sample(-100:100, 5, replace=FALSE)
print(coeffs)
```


- Determine the lenght of coeffs
```{r}
print(length(coeffs))
```

